The classical mutual information in mean-field spin glass models

### 2015-05-26 sk_model_v15.tex
initial version
Stephen's first edits -- need to change Fig.1 and add MC methods section

\author{Vincenzo Alba}
\affiliation{International School for Advanced Studies (SISSA),
Via Bonomea 265, 34136, Trieste, Italy, 
INFN, Sezione di Trieste}
\author{Stephen Inglis}
\affiliation{Department of Physics and Arnold Sommerfeld
Center for Theoretical Physics, Ludwig-Maximilians-Universit\"at
M\"unchen, D-80333 M\"unchen, Germany}
%\author{Lode Pollet}

@@

We investigate the \emph{classical} R\'enyi entropy $S_n$ and the associated mutual 
information ${\mathcal I}_n$ in the Sherrington-Kirkpatrick (S-K) model, which is the 
paradigm model of mean-field spin glasses. We use both classical Monte Carlo simulations 
and analytical tools. First, we investigate the S-K model on the $n$-sheets booklet. This 
is obtained by gluing together $n$ independent copies of the model, and it is the 
main ingredient to construct entaglement-related quantities. We find that at low temperature 
the S-K model is in a glassy phase, whereas at high temperature it exhibits paramagnetic 
behavior. Interestingly, the critical temperature of the paramagnetic-glassy transition 
depends in a non-trivial way on the geometry of the booklet. At high-temperatures we provide 
the exact solution of the model exploiting the replica symmetry. This is the permutation 
symmetry among the fictitious replicas that are used in the replica trick to perform disorder 
averages. In the low-temperature glassy phase the replica symmetry has 
to be broken. Using a simple generalization of the celebrated Parisi solution, we provide 
approximated results for thermodynamic quantities and for $S_n$ and ${\mathcal I}_n$. 
Finally, we show that both $S_n$ and ${\mathcal I}_n$ exhibit a volume law in the whole phase 
diagram. Their densities $S_n/N$ and ${\mathcal I}_n/N$ are finite and smooth 
function of the temperature, in the thermodynamic limit. In contrast with local spin models, 
${\mathcal I}_n/N$ does not exhibit any crossing for different system sizes at the 
critical point.

@@

Besides being ubiquitous in nature, disorder leads to several intriguing 
physical phenomena. Arguably, \emph{spin glasses} provide one of the most 
striking examples. While at any finite temperature disorder prevents the 
usual magnetic ordering, at low-enough temperatures these systems display a 
new and exotic type of ``order''. In the past decades an intense theoretical 
effort has been devoted to characterizing this spin glass order, the nature of 
the paramagnetic-glassy transition, and that of the associated order 
parameter~\cite{binder-1986,parisi-book,young-1998,nishimori-book,castellani-2005}.

@@

In the last decade entanglement-related quantities have emerged as valuable tools to 
understand the physics of complex systems~\cite{amico-2008,eisert-2009,calabrese-2009,
cc-rev}, both classical and quantum. For instance, at a conformally invariant critical 
point entanglement measures contain universal information about the underlying 
conformal field theory (CFT), such as the central charge~\cite{holzhey-1994,vidal-2003,
calabrese-2004,calabrese-2012}. For classical spin models a lot of attention has been 
focused on the \emph{classical} R\'enyi entropy~\cite{jaconis-2013,stephan-2014}. Given 
a bipartition of the system into two complementary subregions $A$ and $B$, the classical 
R\'enyi entropy $S_n(A)$ (with $n\in\mathbb{N}$) is defined as 
%
\begin{equation}
S_n(A)\equiv \frac{1}{1-n}\log\Big(\sum\limits_{i_A\in{\mathcal C}_A} p^n_{i_A}
\Big).i 
\label{renyi-intro}
\end{equation}
%
Here ${\mathcal C}_A$ denotes the set of all the possible spin configurations in part 
$A$, whereas $p_{i_A}$ is the probability of the configuration $i_A$. 
%Clearly, $p_{i_A}\equiv\sum_{j_b\in{\mathcal C}_B}p_{i_A,j_B}$, with $p_{i_A,j_B}$ 
%being the probability that the system is in the configuration $i_A\in{\mathcal C}_A$
%in part $A$, and $j_B\in{\mathcal C}_B$ in part $B$. For a spin model at inverse 
%temperature $\beta$, one has $p_{i_A,j_B}\equiv e^{-\beta E(i_A,j_B)}/Z(\beta)$, 
%where $E(i_A,j_B)$ is the energy of the system, and $Z(\beta)$ its partition function. 
Alternatively, $S_n(A)$ can be obtained from the partition function of the model on 
an \emph{ad hoc} defined ``booklet'' geometry (see section~\ref{booklet} for its 
precise definition). This consists of $n$ independent and identical replicas (the 
booklet ``sheets'') of the model. Notice that these \emph{physical} replicas are different 
from the \emph{fictitious} ones used to perform the disorder average. Each sheet is 
divided into two parts $A$ and $B$, containing $N_A$ and $N_B$ spins, respectively. 
The spins in part $A$ of different sheets are constrained to be equal. It is 
convenient to introduce the aspect ratio $0\le\omega\le1$ as  
%
\begin{equation}
\label{a-ratio}
\omega\equiv \frac{N_A}{N}.
\end{equation}
%
Clearly,  Eq.~\eqref{renyi-intro} can be extended to quantum systems~\cite{stephan-2009,
stephan-2010,stephan-2011,zaletel-2011,alcaraz-2013,stephan-2014-a} by interpreting 
$p_{i_A}$ as the probability of finding part $A$ in the \emph{quantum} configuration 
$i_A$. From $S_n(A)$, one defines the classical mutual information ${\mathcal I}_n(A,B)$ 
as 
%
\begin{equation}
{\mathcal I}_n(A,B)\equiv S_n(A)+S_n(B)-S_n(A\cup B). 
\end{equation}
%
For local models ${\mathcal I}_n$ obeys the area law~\cite{wolf-2008} ${\mathcal I}_n(A)
\propto\ell$, with $\ell$ being the length of the boundary between $A$ and $B$. Remarkably, 
for different $\ell$, the ratio ${\mathcal I}_n/\ell$ exhibits a crossing at a second 
order phase transition~\cite{jaconis-2013}, and it can be used as a diagnostic tool for 
critical behaviors. For conformally invariant critical models more universal information 
can be extracted from the subleading contributions, i.e., the corrections to the area 
law, of ${\mathcal I}_n$~\cite{stephan-2014}.

Recently, the study of the interplay between disorder and entanglement became a fruitful 
research area~\cite{refael-2009}. However, the behavior of entanglement-related quantities 
in glassy phases, and at glassy critical points, has not been explored yet. Here we investigate 
both the classical R\'enyi entropy $S_n(A)$ and the mutual information ${\mathcal I}_n$ 
in the S-K model, using classical Monte Carlo simulations and analytical tools. We often 
restrict ourselves to the case with $n=2$. As usual in disordered system, we 
focus on disorder-averaged quantities, considering $[S_n]$ and $[{\mathcal I}_n]$, 
with the brackets $[\cdot]$ denoting the average over different realizations of 
$J_{ij}$ in Eq.~\eqref{SK-intro}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%e
\begin{figure}[t]
\includegraphics*[width=0.93\linewidth]{./draft_figs/cartoon}
\caption{ The booklet geometry considered in this work. (a) The single sheet 
 (``page'') of the booklet: The $N$ spins living on the sheet are divided into 
 two groups $A$ and $B$, containing $N_A$ and $N_B$ spins, respectively. Here 
 $\omega\equiv N_A/N$ is the booklet ratio. (b) The $n$ sheets are glued together 
 to form the booklet. The spins in part $B$ of the booklet pages are at inverse 
 temperature $\beta$. The spins in part $A$ are identified  (see Eq.~\eqref{book-constraint}). 
 As a consequence, the effective temperature in part $A$ is $n\beta$. 
 $Z(\omega,n,\beta)$ denotes the partition function of the S-K model on 
 the booklet. 
}
\label{cartoon}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

This scenario, and, in particular, the effects of the replica symmetry breaking, are 
reflected in the behavior of $[S_2]$ and $[{\mathcal I}_2]$. First, since $[S_2]$ exhibits 
the volume law behavior $[S_2]\propto N$, we consider its density $[S_2]/N$. For finite-size 
systems, and for any $\omega$, we find that $[S_2]/N$ exhibits a maximum at infinite 
temperature, and it is a monotonically decreasing function of the temperature. More 
specifically, the Monte Carlo data suggest a vanishing behavior in the zero-temperature 
limit. Moreover, the finite-size corrections are neglegible at high temperatures, 
whereas they increase upon lowering the temperature. A standard finite-size scaling 
analysis shows that in the thermodynamic limit $[S_2]/N$ is finite and smooth as a 
function of $\beta$ and $\omega$, in the whole phase diagram. In the paramagnetic phase 
we are able to calculate the functional form of $[S_2]$, using the replica-symmetric 
approximation. This perfectly matches the Monte Carlo data. At low temperatures deviations 
from the replica-symmetric result are observed, reflecting the replica symmetry breaking. 
Remarkably, we observe that the one-step replica symmetry breaking ($1$-RSB) approximation 
$S_2^{1\textrm{-}RSB}/N$ is in full agreement with the Monte Carlo data for $\beta
\lesssim 3$, confirming what is observed for the internal energy.

Finally, we consider the R\'enyi mutual information $[{\mathcal I}_2]$. This  
obeys a volume law for any $\beta$ and $\omega$, in sharp contrast with local spin models, 
where an area law is observed~\cite{wolf-2008}. The mutual information density $[{\mathcal I}_2]/N$ 
vanishes in both the infinite-temperature and the zero-temperature limits, for any $\omega$. 
Surprisingly, for different sizes ${\mathcal I}_2/N$ does not exhibit any crossing at the 
paramagnetic-glassy transition, in striking contrast with local spin models~\cite{jaconis-2013}. 
In the thermodynamic limit $[{\mathcal I}_2]/N$ is finite and smooth (as a function of $\beta$) 
in the whole phase diagram. Interestingly, for any $\omega$, ${\mathcal I}_2/N$ exhibits a 
maximum for $\beta\approx 1$. However, the position of this maximum is not simply related to 
paramagnetic-glassy transition. Finally, at high temperature $[{\mathcal I}_2]/N$ is fully 
described analytically within the replica symmetric approximation, whereas at low temperatures 
one has to include  the effects of the replica symmetry breaking. Similar to $[S_2]$, we observe 
that the $1$-RSB approximation for $[{\mathcal I})_2]/N$, is in good agreement with the Monte Carlo 
data for $\beta\approx 3$.

@@

Given a generic \emph{classical} spin model at inverse temperature $\beta$, 
the R\'enyi mutual information ${\mathcal I}_n(A,B,\beta)$ (with $n\in\mathbb{N}$) 
is defined as~\cite{jaconis-2013,stephan-2014} 
%
\begin{equation}
\label{MI}
{\mathcal I}_n(A,B,\beta)\equiv\frac{1}{1-n}\log\Big(
\frac{Z(A,n,\beta)Z(B,n,\beta)}{Z(\beta)^nZ(n\beta)}
\Big).
\end{equation}
%
Here $Z(A,n,\beta)$ is the partition function of the model on the so-called 
$n$-sheet booklet, whereas $Z(\beta)$ and $Z(n\beta)$ are the partition functions 
on a the plane (a single sheet) at inverse temperatures $\beta$ and $n\beta$, 
respectively. The booklet geometry is illustrated in Figure~\ref{cartoon}. The 
sheet is divided into two parts $A$ and $B$ (cf. Figure~\ref{cartoon} (a)). 
Then $n$ copies of the system (``sheets'') are ``glued'' together to form the 
booklet. The spins in part $A$ of different sheets are identified (cf. 
Figure~\ref{cartoon} (b)). Notice that a similar construction~\cite{guerra-2002} 
plays an important role in the mathematical proof of the Parisi ansats. While spins 
in $B$ are at inverse temperature $\beta$, the ones in $A$ are at the effective 
temperature $n\beta$. The definition of $Z(B,n\beta)$ is obtained by exchanging 
$A$ and $B$. Alternatively, ${\mathcal I}_n$ can be rewritten as 
%
\begin{equation}
{\mathcal I}_n(A,B,\beta)=S_n(A)+S_n(B)-S_n(A\cup B),
\end{equation}
%
where $S_n(X)$ is the ``booklet'' classical R\'enyi entropy
%
\begin{equation}
\label{renyi}
S_n(X)\equiv \frac{1}{1-n}\log\left(\frac{Z(X,n,\beta)}{Z^n(\beta)}\right).
\end{equation}
%
Notice that $S_n(X)$ corresponds to $S_n(X)\equiv1/(n-1)\log(F(X,n,\beta))
-n\log(F(\beta))$, where $F(X,n,\beta)\equiv\log(Z(\beta))$ and $F(\beta)
\equiv\log(Z(X,n,\beta))$ are related (apart from a factor $\beta$) to the 
free energy of the model on the booklet and on the plane, respectively.
Since here we focus on the effects of the disorder, we consider 
the disorder-averaged mutual information $[{\mathcal I}_n]$ 
%
\begin{equation}
[{\mathcal I}_n(A,B,\beta)]=[S_n(A)]+[S_n(B)]-[S_n(A\cup B)],
\end{equation}
%
where the square brackets $[\cdot]$ denote the average over different disorder 
realizations (cf. section~\ref{the-model}). Notice that $[{\mathcal I}_n]$ is 
directly obtained from the so-called quenched averaged free energy $[F(X,n,\beta)]$, 
which is usually considered in disordered systems~\cite{cardy-book}.

@@

The Sherrington-Kirkpatrick (S-K) model~\cite{sherrington-1978-prl,
sherrington-1978} on the $n$-sheets booklet (cf. Figure~\ref{cartoon}) is 
defined by the Hamiltonian
%
\begin{equation}
{\mathcal H}=-\sum\limits_{r=1}^n\left\{\sum\limits_{i<j}J_{ij}S^{(r)}_i 
S^{(r)}_j-h\sum\limits_{i=1}^NS^{(r)}_i\right\}.
\label{SK-ham}
\end{equation}
%
Here $S_i^{(r)}=\pm 1$ are classical Ising spins, $r\in[1,n]$ labels the 
different sheets (``pages'') of the booklet, $i\in[1,N]$ denotes the sites on 
each sheet, $J_{ij}$ is the interaction strength, and $h$ is an external 
magnetic field. Here we choose $h=0$. The total number of spins in the booklet 
is $nN$. The first sum inside the brackets in Eq.~\eqref{SK-ham} is over all the 
$N(N-1)/2$ pairs of spins in each sheet. Spins on different sheets do not interact. 
In each ``page''  all the sites are divided into two groups $A\equiv\{1,\dots, 
N_A\}$ and $B\equiv\{N_A+1,\dots,N\}$, containing $N_A$ and $N_B\equiv N-N_A$ 
sites, respectively. The spins living in part $A$ and different sheets 
are identified, i.e., $\forall i\in A$ one has  
%
\begin{equation}
S_i^{(r)}=S_{i}^{(r')}\quad\forall\, r,r'. 
\label{book-constraint}
\end{equation}
%
Since in each sheet all spins interact with each other, there is no notion of distance. 
between different spins. Thus, physical observables should depend on the booklet geometry 
only through the ratio $\omega\equiv N_A/N_B$.

@@

In this section we present the solution of the S-K model on the booklet, using 
the replica symmetric approximation. In subsection~\ref{para-section} we focus 
on the paramagnetic phase at high temperature, where this approximation is exact. 
In particular, we show that the behavior of the model is fully determined by the 
diagonal part of the overlap tensor $q_{\gamma\gamma'}^{rr'}$. The general structure 
of $q_{\gamma\gamma'}^{rr'}$ in the replica-symmetric (RS) ansatz  is discussed in 
subsection~\ref{rs-section}. This allows to determine the critical temperature of 
the paramagnetic-glassy transition. Similar to the standard S-K model, the RS ansatz 
is not correct in the low-temperature region.

@@

Finally, using the replica-symmetric ansatz Eq.~\eqref{rs-ansatz} one can determine 
the critical temperature $\beta_c$ of the paramagnetic-glassy transition. 
Near the glassy transition one should expect $q'_0\to0$, whereas $q_0$ 
should remain finite ($q_0>0$ in the paramagnetic phase, see section~\ref{para-section}). 
By expanding $[F_{RS}(\omega,n,\beta)]$ (cf. Eq~\eqref{rs-F}) for small $q_0'$, and 
keeping only terms up to ${\mathcal O}((q_0')^2$, one obtains a standard Landau theory. 
Thus, $\beta_c$ is obtained imposing that the coefficient of the quadratic term $q_0'^2$ 
changes sign. This leads to the equation 
%
\begin{equation}
\exp(-4q_0\beta^2_c)+2\exp(-2q_0\beta^2_c)=\frac{1-4\beta^2_c}
{4\beta^2_c\omega-1},
\label{tc}
\end{equation}
%
where $q_0$ is obtained by solving the high-temperature saddle point 
equation~\eqref{saddle-high-t}. The resulting $\beta_c$ solution of Eq.~\eqref{tc} 
is shown in Fig.~\ref{beta_c} as a function of $\omega$.

@@

We now turn to discuss the behavior of the classical R\'enyi entropies (cf. 
Eq.~\eqref{renyi}) in the S-K model. Here we restrict ourselves to the second R\'enyi 
entropy $S_2$. Due to the mean-field nature of the S-K model (cf. Eq.~\eqref{SK-ham}), 
there is no boundary between the two parts $A$ and $B$ of the system (see Fig.~\ref{cartoon}), 
implying that $S_2$ exhibits the volume law $S_2\propto N$, rather than the area law. 
Therefore it is natural to consider the entropy per spin $S_2/N$.

>>>>

\author{Vincenzo Alba}
\affiliation{International School for Advanced Studies (SISSA),
Via Bonomea 265, 34136, Trieste, Italy, 
INFN, Sezione di Trieste}
\author{Stephen Inglis}
\affiliation{Department of Physics and Arnold Sommerfeld
Center for Theoretical Physics, Ludwig-Maximilians-Universit\"at
M\"unchen, D-80333 M\"unchen, Germany}
\author{Lode Pollet}
\affiliation{Department of Physics and Arnold Sommerfeld
    Center for Theoretical Physics, Ludwig-Maximilians-Universit\"at
M\"unchen, D-80333 M\"unchen, Germany}

@@

We investigate the \emph{classical} R\'enyi entropy $S_n$ and the associated mutual 
information ${\mathcal I}_n$ in the Sherrington-Kirkpatrick (S-K) model, which is the 
paradigm model of mean-field spin glasses. 
Using both classical Monte Carlo simulation and analytical tools we investigate the S-K model 
on a booklet of $n$-sheets.
This is obtained by gluing together $n$ independent copies of the model, and it is the 
main ingredient to construct the R\'enyi entaglement-related quantities. We find that at low temperature 
the S-K model is in a glassy phase, whereas at high temperature it exhibits paramagnetic 
behavior. Interestingly, the critical temperature of the paramagnetic-glassy transition 
depends in a non-trivial way on the geometry of the booklet. At high-temperatures we provide 
the exact solution of the model exploiting the replica symmetry. This is the permutation 
symmetry among the fictitious replicas that are used in the replica trick to perform disorder 
averages. In the low-temperature glassy phase the replica symmetry has 
to be broken. Using a generalization of the celebrated Parisi solution, we provide 
approximated results for thermodynamic quantities and for $S_n$ and ${\mathcal I}_n$. 
Finally, we show that both $S_n$ and ${\mathcal I}_n$ exhibit a volume law in the whole phase 
diagram. Their densities $S_n/N$ and ${\mathcal I}_n/N$ are finite and smooth 
function of the temperature, in the thermodynamic limit. In contrast with local spin models, 
${\mathcal I}_n/N$ does not exhibit any crossing for different system sizes at the 
critical point.

@@

Besides being ubiquitous in nature, disorder leads to several intriguing 
physical phenomena. 
Arguably, \emph{spin glasses} represent one of the most prototypical examples
of disorder.
While at any finite temperature disorder prevents the 
usual magnetic ordering, at low-enough temperatures these systems display a 
new and exotic type of ``order''. In the past decades an intense theoretical 
effort has been devoted to characterizing this spin glass order, the nature of 
the paramagnetic-glassy transition, and that of the associated order 
parameter~\cite{binder-1986,parisi-book,young-1998,nishimori-book,castellani-2005}.

@@

In the last decade entanglement-related quantities have emerged as valuable tools to 
understand the physics of complex systems~\cite{amico-2008,eisert-2009,calabrese-2009,
cc-rev}, both classical and quantum. For instance, at a conformally invariant critical 
point entanglement measures contain universal information about the underlying 
conformal field theory (CFT), such as the central charge~\cite{holzhey-1994,vidal-2003,
calabrese-2004,calabrese-2012}. For classical spin models a lot of attention has been 
focused on the \emph{classical} R\'enyi entropy~\cite{jaconis-2013,stephan-2014}. Given 
a bipartition of the system into two complementary subregions $A$ and $B$, the classical 
R\'enyi entropy $S_n(A)$ (with $n\in\mathbb{N}$) is defined as 
%
\begin{equation}
S_n(A)\equiv \frac{1}{1-n}\log\Big(\sum\limits_{i_A\in{\mathcal C}_A} p^n_{i_A}
\Big)
\label{renyi-intro}
\end{equation}
%
Here ${\mathcal C}_A$ denotes the set of all the possible spin configurations in part 
$A$, whereas $p_{i_A}$ is the probability of the configuration $i_A$. 
%Clearly, $p_{i_A}\equiv\sum_{j_b\in{\mathcal C}_B}p_{i_A,j_B}$, with $p_{i_A,j_B}$ 
%being the probability that the system is in the configuration $i_A\in{\mathcal C}_A$
%in part $A$, and $j_B\in{\mathcal C}_B$ in part $B$. For a spin model at inverse 
%temperature $\beta$, one has $p_{i_A,j_B}\equiv e^{-\beta E(i_A,j_B)}/Z(\beta)$, 
%where $E(i_A,j_B)$ is the energy of the system, and $Z(\beta)$ its partition function. 
Alternatively, $S_n(A)$ can be obtained from the partition function of the model on 
an \emph{ad hoc} defined ``booklet'' geometry (see section~\ref{booklet} for its 
precise definition). This consists of $n$ independent and identical replicas (the 
booklet ``sheets'') of the model. Notice that these \emph{physical} replicas are different 
from the \emph{fictitious} ones used to perform the disorder average. Each sheet is 
divided into two parts $A$ and $B$, containing $N_A$ and $N_B$ spins, respectively. 
The spins in part $A$ of different sheets are constrained to be equal. It is 
convenient to introduce the aspect ratio $0\le\omega\le1$ as  
%
\begin{equation}
\label{a-ratio}
\omega\equiv \frac{N_A}{N}.
\end{equation}
%
Clearly,  Eq.~\eqref{renyi-intro} can be extended to quantum systems~\cite{stephan-2009,
stephan-2010,stephan-2011,zaletel-2011,alcaraz-2013,stephan-2014-a} by interpreting 
$p_{i_A}$ as the probability of finding part $A$ in the \emph{quantum} configuration 
$i_A$. From $S_n(A)$, one defines the classical mutual information ${\mathcal I}_n(A,B)$ 
as 
%
\begin{equation}
{\mathcal I}_n(A,B)\equiv S_n(A)+S_n(B)-S_n(A\cup B). 
\end{equation}
%
For local models ${\mathcal I}_n$ obeys the area law~\cite{wolf-2008} ${\mathcal I}_n(A)
\propto\ell$, with $\ell$ being the length of the boundary between $A$ and $B$. Remarkably, 
for different $\ell$, the ratio ${\mathcal I}_n/\ell$ exhibits a crossing at a second 
order phase transition~\cite{jaconis-2013}, and it can be used as a diagnostic tool for 
critical behaviors. For conformally invariant critical models more universal information 
can be extracted from the subleading contributions, i.e., the corrections to the area 
law, of ${\mathcal I}_n$~\cite{stephan-2014}.

Recently, the study of the interplay between disorder and entanglement became a fruitful 
research area~\cite{refael-2009}. However, the behavior of entanglement-related quantities 
in glassy phases, and at glassy critical points, has not been explored yet. Here we investigate 
both the classical R\'enyi entropy $S_n(A)$ and the mutual information ${\mathcal I}_n$ 
in the S-K model, using classical Monte Carlo simulations and analytical tools. We often 
restrict ourselves to the case with $n=2$, as this is where numerical simulation is most
efficient . As usual in disordered system, we 
focus on disorder-averaged quantities, considering $[S_n]$ and $[{\mathcal I}_n]$, 
with the brackets $[\cdot]$ denoting the average over different realizations of 
$J_{ij}$ in Eq.~\eqref{SK-intro}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%e
\begin{figure}[t]
\includegraphics*[width=0.93\linewidth]{./draft_figs/cartoon}
\caption{ The booklet geometry considered in this work. (a) The single sheet 
 (``page'') of the booklet: The $N$ spins living on the sheet are divided into 
 two groups $A$ and $B$, containing $N_A$ and $N_B$ spins, respectively. Here 
 $\omega\equiv N_A/N$ is the booklet ratio. (b) The $n$ sheets are glued together 
 to form the booklet. The spins in part $B$ of the booklet pages are at inverse 
 temperature $\beta$. The spins in part $A$ are identified  (see Eq.~\eqref{book-constraint}). 
 As a consequence, the effective temperature in part $A$ is $n\beta$. 
 $Z(A,n,\beta)$ denotes the partition function of the S-K model on 
 the booklet. 
}
\label{cartoon}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In this scenario the effects of the replica symmetry breaking are 
reflected in the behavior of $[S_2]$ and $[{\mathcal I}_2]$. First, since $[S_2]$ exhibits 
the volume law behavior $[S_2]\propto N$, we consider its density $[S_2]/N$. For finite-size 
systems, and for any $\omega$, we find that $[S_2]/N$ exhibits a maximum at infinite 
temperature, and it is a monotonically decreasing function of the temperature. More 
specifically, the Monte Carlo data suggest a vanishing behavior in the zero-temperature 
limit. Moreover, the finite-size corrections are neglegible at high temperatures, 
whereas they increase upon lowering the temperature. A standard finite-size scaling 
analysis shows that in the thermodynamic limit $[S_2]/N$ is finite and smooth as a 
function of $\beta$ and $\omega$, in the whole phase diagram. In the paramagnetic phase 
we are able to calculate the functional form of $[S_2]$, using the replica-symmetric 
approximation. This perfectly matches the Monte Carlo data. At low temperatures deviations 
from the replica-symmetric result are observed, reflecting the replica symmetry breaking. 
Remarkably, we observe that the one-step replica symmetry breaking ($1$-RSB) approximation 
$S_2^{1\textrm{-}RSB}/N$ is in full agreement with the Monte Carlo data for $\beta
\lesssim 3$, confirming what is observed for the internal energy.

Finally, we consider the R\'enyi mutual information $[{\mathcal I}_2]$. This  
obeys a volume law for any $\beta$ and $\omega$, in sharp contrast with local spin models, 
where an area law is observed~\cite{wolf-2008}. The mutual information density $[{\mathcal I}_2]/N$ 
vanishes in both the infinite-temperature and the zero-temperature limits, for any $\omega$. 
Surprisingly, for different sizes ${\mathcal I}_2/N$ does not exhibit any crossing at the 
paramagnetic-glassy transition, in striking contrast with local spin models~\cite{jaconis-2013}. 
In the thermodynamic limit $[{\mathcal I}_2]/N$ is finite and smooth (as a function of $\beta$) 
in the whole phase diagram. Interestingly, for any $\omega$, ${\mathcal I}_2/N$ exhibits a 
maximum for $\beta\approx 1$. However, the position of this maximum is not simply related to 
paramagnetic-glassy transition. Finally, at high temperature $[{\mathcal I}_2]/N$ is fully 
described analytically within the replica symmetric approximation, whereas at low temperatures 
one has to include  the effects of the replica symmetry breaking. Similar to $[S_2]$, we observe 
that the $1$-RSB approximation for $[{\mathcal I})_2]/N$, is in good agreement with the Monte Carlo 
data for $\beta \lesssim 3$.

@@

Given a generic \emph{classical} spin model at inverse temperature $\beta$, 
the R\'enyi mutual information ${\mathcal I}_n(A,B,\beta)$ (with $n\in\mathbb{N}$
and $A \cup B$ is the entire system)) 
is defined as~\cite{jaconis-2013,stephan-2014} 
%
\begin{equation}
\label{MI}
{\mathcal I}_n(A,B,\beta)\equiv\frac{1}{1-n}\log\Big(
\frac{Z(A,n,\beta)Z(B,n,\beta)}{Z(\beta)^nZ(n\beta)}
\Big).
\end{equation}
%
Here $Z(A,n,\beta)$ is the partition function of the model on the so-called 
$n$-sheet booklet, whereas $Z(\beta)$ and $Z(n\beta)$ are the partition functions 
on a the plane (a single sheet) at inverse temperatures $\beta$ and $n\beta$, 
respectively. The booklet geometry is illustrated in Figure~\ref{cartoon}. The 
sheet is divided into two parts $A$ and $B$ (cf. Figure~\ref{cartoon} (a)). 
Then $n$ copies of the system (``sheets'') are ``glued'' together to form the 
booklet. The spins in part $A$ of different sheets are identified (cf. 
Figure~\ref{cartoon} (b)). Notice that a similar construction~\cite{guerra-2002} 
plays an important role in the mathematical proof of the Parisi ansats. While spins 
in $B$ are at inverse temperature $\beta$, the ones in $A$ are at the effective 
temperature $n\beta$. The definition of $Z(B,n,\beta)$ is obtained by exchanging 
$A$ and $B$. Alternatively, ${\mathcal I}_n$ can be rewritten as 
%
\begin{equation}
{\mathcal I}_n(A,B,\beta)=S_n(A)+S_n(B)-S_n(A\cup B),
\end{equation}
%
where $S_n(X)$ is the ``booklet'' classical R\'enyi entropy
%
\begin{equation}
\label{renyi}
S_n(X)\equiv \frac{1}{1-n}\log\left(\frac{Z(X,n,\beta)}{Z^n(\beta)}\right).
\end{equation}
%
Notice that $S_n(X)$ corresponds to $S_n(X)\equiv1/(n-1)\log(F(X,n,\beta))
-n\log(F(\beta))$, where $F(X,n,\beta)\equiv\log(Z(X,n\beta))$ and $F(\beta)
\equiv\log(Z(\beta))$ are related (apart from a factor $\beta$) to the 
free energy of the model on the booklet and on the plane, respectively.
Since here we focus on the effects of the disorder, we consider 
the disorder-averaged mutual information $[{\mathcal I}_n]$ 
%
\begin{equation}
[{\mathcal I}_n(A,B,\beta)]=[S_n(A)]+[S_n(B)]-[S_n(A\cup B)],
\end{equation}
%
where the square brackets $[\cdot]$ denote the average over different disorder 
realizations (cf. section~\ref{the-model}). Notice that $[{\mathcal I}_n]$ is 
directly obtained from the so-called quenched averaged free energy $[F(X,n,\beta)]$, 
which is usually considered in disordered systems~\cite{cardy-book}.

@@

The Sherrington-Kirkpatrick (S-K) model~\cite{sherrington-1978-prl,
sherrington-1978} on the $n$-sheets booklet (cf. Figure~\ref{cartoon}) is 
defined by the Hamiltonian
%
\begin{equation}
{\mathcal H}=-\sum\limits_{r=1}^n\left\{\sum\limits_{i<j}J_{ij}S^{(r)}_i 
S^{(r)}_j-h\sum\limits_{i=1}^NS^{(r)}_i\right\}.
\label{SK-ham}
\end{equation}
%
Here $S_i^{(r)}=\pm 1$ are classical Ising spins, $r\in[1,n]$ labels the 
different sheets (``pages'') of the booklet, $i\in[1,N]$ denotes the sites on 
each sheet, $J_{ij}$ is the interaction strength, and $h$ is an external 
magnetic field. Here we choose $h=0$. The total number of spins in the booklet 
is $nN$. The first sum inside the brackets in Eq.~\eqref{SK-ham} is over all the 
$N(N-1)/2$ pairs of spins in each sheet. Spins on different sheets do not interact. 
In each ``page''  all the sites are divided into two groups $A\equiv\{1,\dots, 
N_A\}$ and $B\equiv\{N_A+1,\dots,N\}$, containing $N_A$ and $N_B\equiv N-N_A$ 
sites, respectively. The spins living in part $A$ and different sheets 
are identified, i.e., $\forall i\in A$ one has  
%
\begin{equation}
S_i^{(r)}=S_{i}^{(r')}\quad\forall\, r,r'. 
\label{book-constraint}
\end{equation}
%
Since in each sheet all spins interact with each other, there is no notion of distance 
between different spins. Thus, physical observables should depend on the booklet geometry 
only through the ratio $\omega\equiv N_A/N$.

@@

In this section we present the solution of the S-K model on the booklet, using 
the replica symmetric approximation. In subsection~\ref{para-section} we focus 
on the paramagnetic phase at high temperature, where this approximation is exact. 
In particular, we show that the behavior of the model is fully determined by the 
diagonal part of the overlap tensor $q_{\gamma\gamma'}^{rr'}$. The general structure 
of $q_{\gamma\gamma'}^{rr'}$ in the replica-symmetric (RS) ansatz  is discussed in 
subsection~\ref{rs-section}. This allows us to determine the critical temperature of 
the paramagnetic-glassy transition. Similar to the standard S-K model, the RS ansatz 
is not correct in the low-temperature region.

@@

Finally, using the replica-symmetric ansatz Eq.~\eqref{rs-ansatz} one can determine 
the critical temperature $\beta_c$ of the paramagnetic-glassy transition. 
Near the glassy transition one should expect $q'_0\to0$, whereas $q_0$ 
should remain finite ($q_0>0$ in the paramagnetic phase, see section~\ref{para-section}). 
By expanding $[F_{RS}(\omega,n,\beta)]$ (cf. Eq~\eqref{rs-F}) for small $q_0'$, and 
keeping only terms up to ${\mathcal O}((q_0')^2)$, one obtains a standard Landau theory. 
Thus, $\beta_c$ is obtained imposing that the coefficient of the quadratic term $q_0'^2$ 
changes sign. This leads to the equation 
%
\begin{equation}
\exp(-4q_0\beta^2_c)+2\exp(-2q_0\beta^2_c)=\frac{1-4\beta^2_c}
{4\beta^2_c\omega-1},
\label{tc}
\end{equation}
%
where $q_0$ is obtained by solving the high-temperature saddle point 
equation~\eqref{saddle-high-t}. The resulting $\beta_c$ solution of Eq.~\eqref{tc} 
is shown in Fig.~\ref{beta_c} as a function of $\omega$.

@@

We now turn to discuss the behavior of the classical R\'enyi entropies (cf. 
Eq.~\eqref{renyi}) in the S-K model. Here we restrict ourselves to the second R\'enyi 
entropy $S_2$. Due to the mean-field nature of the S-K model (cf. Eq.~\eqref{SK-ham}), 
there is no well defined boundary between the two parts $A$ and $B$ of the system (unlike Fig.~\ref{cartoon} for local models).
The fully connected nature of the model suggests that $S_2$ should be volume law $S_2 \propto N$ for all temperature.
Therefore it is natural to consider the entropy per spin $S_2/N$.
